DATA 621 Homework #5

### 2019-12-05 hw5/HW5_Mike.Rmd
More work

@@

```{r}
train1 <- train %>%
  select(-LabelAppeal, -AcidIndex, -STARS, -STARS_imputed)
model1 <- glm(TARGET ~ ., family = quasipoisson, train1)
summary(model1)
```

>>>>

### Setting Up Evaluation

In order to assess the models we will assume that a bottle of wine whosale costs $15.00 and there are 10 bottles in a case.  We will assume that the `TARGET` is the maximum amount that will sell in the market.  Any predictions below the `TARGET` represent potential revenue that is unrealized.  Any predictions over the `TARGET` will not sell and represent a loss of $150.  We will evaluate the model to see if it helps the manufacturers goal of maximizing revenue.

```{r}
evaluate_model <- function(model, test_df, yhat = FALSE){
  price_per_bottle <- 15.00
  bottles_per_case <- 10
  case_price <- price_per_bottle * bottles_per_case
  temp <- data.frame(yhat=c(0:8), TARGET = c(0:8), n=c(0))

  if(yhat){
    test_df$yhat <- yhat
  } else {
    test_df$yhat <- round(predict.glm(model, newdata=test_df, type="response"), 0)
  }

  test_df <- test_df %>%
    group_by(yhat, TARGET) %>%
    tally() %>%
    mutate(accuracy = ifelse(yhat > TARGET, "Over", ifelse(yhat < TARGET, "Under", "Accurate"))) %>%
    mutate(off_by = abs(yhat - TARGET)) %>%
    mutate(revenue = ifelse(off_by == 0, 1, -1) * n * case_price)

  rev_df <- test_df %>%
    group_by(accuracy) %>%
    summarise(revenue = sum(revenue)) %>%
    spread(accuracy, revenue)

  total_rev <- sum(test_df$revenue)

  results <- test_df %>%
    group_by(accuracy) %>%
    summarise(n = sum(n))

  confusion_matrix <- test_df %>%
    bind_rows(temp) %>%
    group_by(yhat, TARGET) %>%
    summarise(n = sum(n)) %>%
    spread(TARGET, n, fill = 0)

  return(list("total_rev" = total_rev, "rev_df" = rev_df, "confusion_matrix" = confusion_matrix, "results" = results))
}
```

### Chemical Property Model

@@

```{r}
train1 <- train %>%
  select(-LabelAppeal, -AcidIndex, -STARS, -STARS_imputed)
model1 <- glm(TARGET ~ ., family = quasipoisson, train1)
summary(model1)
model1_results <- evaluate_model(model1, test)
```

The following is a confusion matrix like examination of the model with the predicted cases going down the rows and the actual cases going across the columns.

```{r}
model1_results$confusion_matrix %>% 
  kable() %>% 
  kable_styling()
```

The model is only accurate `r temp <- model1_results$results %>% filter(accuracy == "Accurate"); temp$n` times.  It overestimates `r temp <- model1_results$results %>% filter(accuracy == "Over"); temp$n` times and underestimates `r temp <- model1_results$results %>% filter(accuracy == "Under"); temp$n` times.  The following shows the revenue gained or lost due to the model's predictions:

```{r}
model1_results$rev_df %>%
  kable() %>%
  kable_styling()
```

This model would result in $`r model1_results$total_rev` in revenue.  The company would loose a lot of money if the model was implemented.

### Second Chemical Property Model

We will try one more chemical property model but only select the variables that were statistically significant in the preious model (`FixedAcidity`, `VolatileAcidity` and `Alcohol`).

```{r}
model2 <- glm(TARGET ~ FixedAcidity + VolatileAcidity + Alcohol, family = quasipoisson, train)
summary(model2)
model2_results <- evaluate_model(model2, test)
```

This model would generate $`r model2_results$total_rev` in revenue.  This is a slight improvement but is still a horible model.  Building a model based off of the chemical properties does not seem like a good solution.  Let's turn our attention to the other variables with stronger correlations.

### Preceived Quality Model

This model relies on the consumer preception of quality based on the label, and the star ratings of the experts.

```{r}
model3 <- glm(TARGET ~ LabelAppeal + STARS, family = quasipoisson, train)
summary(model3)
model3_results <- evaluate_model(model3, test)
```

Here is a confusion matrix for this model:

```{r}
model3_results$confusion_matrix %>% 
  kable() %>% 
  kable_styling()
```

The model is only accurate `r temp <- model3_results$results %>% filter(accuracy == "Accurate"); temp$n` times.  It overestimates `r temp <- model3_results$results %>% filter(accuracy == "Over"); temp$n` times and underestimates `r temp <- model3_results$results %>% filter(accuracy == "Under"); temp$n` times.  This is an improvement from just the chemical property models, however there is still a lot of error.  The following shows the revenue gained or lost due to the model's predictions:

```{r}
model3_results$rev_df %>%
  kable() %>%
  kable_styling()
```

This model would result in $`r model3_results$total_rev` in revenue.

### Perceived Quality Plus Model

We will begin with the preceeding model but add in the Acid Index and the flag if the STARS was imputed.

```{r}
model4 <- glm(TARGET ~ LabelAppeal + STARS + AcidIndex + STARS_imputed, family = quasipoisson, train)
summary(model4)
model4_results <- evaluate_model(model4, test)
```

Let's see how the predictions line up with the reality:

```{r}
model4_results$confusion_matrix %>% 
  kable() %>% 
  kable_styling()
```

The model is accurate `r temp <- model4_results$results %>% filter(accuracy == "Accurate"); temp$n` times.  It overestimates `r temp <- model4_results$results %>% filter(accuracy == "Over"); temp$n` times and underestimates `r temp <- model4_results$results %>% filter(accuracy == "Under"); temp$n` times.  The following shows the revenue gained or lost due to the model's predictions:

```{r}
model4_results$rev_df %>%
  kable() %>%
  kable_styling()
```

This model would result in $`r model4_results$total_rev` in revenue.  It is the best model so far but it still would loose a lot of money because it overestimates the number of cases to be sold.

There are no zero predictions in this model which is not accurate.  We will try to address this in our last model

### Adjusted Perceived Quality Plus Model

We will start with the predictions from preceived quality plus model.  We will then manually override the the predictions that have the stars filled in with a predicted zero.

```{r}
temp <- test
temp$yhat <- round(predict.glm(model4, newdata=temp, type="response"), 0)
temp <- temp %>%
  mutate(yhat = ifelse(STARS_imputed == 1, 0, yhat))
model5_results <- evaluate_model(model4, test, temp$yhat)
```

```{r}
model5_results$confusion_matrix %>% 
  kable() %>% 
  kable_styling()
```

```{r}
model5_results$rev_df %>%
  kable() %>%
  kable_styling()
```
